MC-Cons: RNA 2D structural assignment

### 2015-07-18 slides/presentation/presentation.tex
working on aknowledgments

\subsection{general workflow}
\begin{frame}
	\frametitle{the workflow}
	\begin{columns}
		\column{0.38\linewidth}
		\centering
		\begin{figure}[!htb]
			\resizebox{1.\textwidth}{!}{\input{workflow.pdf_tex}}
		\end{figure}

        \column{0.58\linewidth}
        \begin{itemize}
        		\item a consensus minimizes the sum of pairs of distances between objects
        		\item optimization steps
        		\begin{enumerate}
        		        			\item base pair structural similarity (modified tree edit distance)
        			\item string edit distance on Vienna dot-bracket representation
        		\end{enumerate}

        \end{itemize}
         \end{columns}

@@

\subsection{matching tree base pairs}
\begin{frame}
	\frametitle{first, we match base pairs structure}
	\begin{figure}[!htb]
	\centering
	\resizebox{0.4\textwidth}{!}{\input{bp_tree.pdf_tex}}
	\end{figure}

	\begin{itemize}
		\item base pair trees created (many-to-one function)
		\item unit tree indel distance calculates number of base pairs to delete or create to transform a tree into another
	\end{itemize}

@@

\subsection{matching strings}
\begin{frame}
	\frametitle{refine by string edit distance}

@@

		\item derivative works
		\begin{itemize}
			\item 3D to 2D tree distance
			\item base pair tree constraints/masks?
		\end{itemize}

@@

\section{Conclusion}

\begin{frame}
	\frametitle{Conclusion}
	\begin{itemize}
		\item Adversarial IR
		\begin{itemize}
			\item it's hard
		\end{itemize}
		\item Link Analysis/Mining
		\begin{itemize}
			\item wide variety of problems and domains
		\end{itemize}
		\item Link Analysis for Web
		\begin{itemize}
			\item Centrality
			\item Pagerank
			\item Topic-sensitive PageRank
			\item Hubs and Authorities
		\end{itemize}
		\item Still many challenges
	\end{itemize}
\end{frame}

@@

>>>>

\subsection{general workflow}
\begin{frame}
	\frametitle{workflow}
	\begin{columns}
		\column{0.38\linewidth}
		\centering
		\begin{figure}[!htb]
			\resizebox{1.\textwidth}{!}{\input{workflow.pdf_tex}}
		\end{figure}

        \column{0.58\linewidth}
        \begin{itemize}
        		\item a consensus minimizes the sum of pairs of distances between objects
        		\item optimization steps
        		\begin{enumerate}
        		        			\item base pair structural similarity (modified tree edit distance)
        			\item string edit distance on Vienna dot-bracket representation
        		\end{enumerate}
			\item two solver in C++ (branch \& bound and genetic algorithm)
        \end{itemize}
         \end{columns}

@@

\subsection{matching base pairs}
\begin{frame}
	\frametitle{first match base pairs}
	\begin{figure}[!htb]
	\centering
	\resizebox{0.4\textwidth}{!}{\input{bp_tree.pdf_tex}}
	\end{figure}

	\begin{itemize}
		\item base pair trees created (many-to-one function)
		\item unit tree indel distance calculates number of base pairs to add or remove to transform a tree into another
	\end{itemize}

@@

\subsection{match the bulges}
\begin{frame}
	\frametitle{then match unpaired}
	\begin{figure}[!htb]
	\centering
	\resizebox{0.75\textwidth}{!}{\input{tree_filtering.pdf_tex}}
	\end{figure}	
	\begin{itemize}
		\item filtered by tree structure, now refine
		\item placing the bulges around the skeleton...
		\item string edit distance on dot-bracket
	\end{itemize}
\end{frame}

@@

		\item derivative works
		\begin{itemize}
			\item base pair tree constraints/masks
			\item 3D to 2D tree distance
		\end{itemize}

@@

\section{recap}

\begin{frame}
	\frametitle{recap}
	\begin{itemize}
		\item MC-Cons creates RNA 2D structural assignment
		\item useful for finding structures explaining function
		\item available at \url{https://github.com/major-lab/MC-Cons}
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Q\&A}
		\url{https://github.com/major-lab/MC-Cons}
\end{frame}
